Debugging by \textit{lastChange}

### 2010-12-10 papers/ecoop2011/ecoop2011-lastChange.tex
edited for correct layout.
updates to related work.

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Ecole Polytechnique F\'ed\'erale de Lausanne \\
\path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
\and IBM Research - Almaden \\
\path|johnjbarton@johnjbarton.com|}

@@

@@

%Leo (the non-det values case), other readers
\subsubsection*{Acknowledgments.} TODO

@@

\bibitem{Barton}%[Bond(2010)]
J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
\newblock In \emph{Conference on World Wide Web(WWW)},
April, 2010.

@@

\bibitem{Bond2}%[Bond(2010)]
M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
June, 2010.

>>>>

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\'Ecole Polytechnique F\'ed\'erale de Lausanne \\
\path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
\and IBM Research - Almaden \\
\path|johnjbarton@johnjbarton.com|}

@@

Bhansali et al. \cite{Bhansali} attempted to attack performance overhead 
and large trace size in their time-travelling debugger, Nirvana. Nirvana 
first collects a full compressed trace of program execution and then 
re-simulate the execution. Their results are quite similar to omniscient 
debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
re-simulation.

@@

%Leo (the non-det values case), other readers
%\subsubsection*{Acknowledgments.} TODO

@@

\bibitem{Barton}
J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
\newblock In \emph{Conference on World Wide Web(WWW)},
April, 2010.

\bibitem{Bhansali}
S. Bhansali, W. Chen, S. de Jong, A. Edwards, R. Murray, M. Drini\'{c}, D. Miho\v{c}ka, J. Chau. \newblock Framework for instruction-level tracing and analysis of program executions.
\newblock In \emph{International Conference on Virtual Execution Environments(VEE)},
June, 2006.

@@

%\bibitem{Bond2}%[Bond(2010)]
%M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
%\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
%June, 2010.
